Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-03 paper/galsize_paper.tex
Completed discussion of Figure 5

@@

A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history. On the other hand, we define a ``true central" as a galaxy that has never been a satellite.

@@

@@

%We conclude this section by estimating how satellite mass stripping manifests in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall evolution of satellites mass and size.

%In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall. The simple interpretation of this assumption is that, in a statistical sense, the size of satellite galaxies is determined by its history as a central galaxy, and that post-infall physics leaves no distinct imprint on satellite $\rhalf.$

%Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_alternate_models.pdf}
\caption{
{\bf Impact of mass loss and orphan satellites.}
Here we compare our fiducial model, \dots 
}
\label{fig:shuffle}
\end{figure}
%-----------------------------------------------------------------------------------------------------

%Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves). The difference between the small-scale clustering of the two models is stark: the assumption that $\rhalf$ decreases after infall leaves a strong imprint on the $\rhalf-$dependence of $\wproj(\rproj),$ such that small galaxies cluster {\em much} more strongly relative to large galaxies, particularly for disk-dominated systems with $\mstar\approx10^{10}\msun.$

%The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}. We refer the reader to \S\ref{subsec:satellite_discussion} for further discussion of the physical implications of this result.

>>>>

\subsection{Size-Dependent Clustering}
\label{subsec:clustering_results}

@@

\subsection{Central vs. Satellite Sizes}
\label{subsec:censat_sizes}

A straightforward resolution to the above puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history. On the other hand, we define a ``true central" as a galaxy that has never been a satellite.

@@

\subsection{Tidal Stripping and Orphan Satellites}
\label{subsec:orphan_stripping}

We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios. In the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations. This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios. The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\rvir-$only model. We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.

The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$only model applied to a subhalo catalog that includes a orphan halos. As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase. We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$only model applied to the resulting catalog.

As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_alternate_models.pdf}
\caption{
{\bf Impact of tidal stripping and orphan satellites.} In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The dashed curves (``$\rvir-$only model") and solid curves (``profile co-evolution model") from  Figure \ref{fig:clustering_ratio_upshot} are also shown for convenience. The dot-dashed curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. The dotted curve shows results for the same model, but including the effect of ``orphan" galaxies that live in subhalos no longer resolved by {\tt Rockstar}. 
}
\label{fig:strippingorphans}
\end{figure}
%-----------------------------------------------------------------------------------------------------
